A Process for the Emulation of Comparative Oncology Trials with Real-world Evidence (ENCORE)

### 2025-02-26 manuscript/manuscript.qmd
decreased size figure 2

```{r}
#| label: fig-initiators
#| fig-cap: "Example visualization of descriptive drug utilization analyses displaying a) initiation trends between compared regimens based on calendar time, b) cumulative rate of patients switching to another line of treatment."
#| fig-widh: 3
#| fig-height: 6
#| fig-pos: 'h'
#| tbl-pos: 'h'

>>>>

```{r}
#| label: fig-initiators
#| fig-cap: "Example visualization of descriptive drug utilization analyses displaying a) initiation trends between compared regimens based on calendar time, b) cumulative rate of patients switching to another line of treatment."
#| fig-widh: 2.5
#| fig-height: 5
#| fig-pos: 'h'
#| tbl-pos: 'h'
